%% LaTeX2e class for student theses
%% sections/introduction.tex
%% 
%% Karlsruhe Institute of Technology
%% Institute of Information Security and Dependability (KASTEL)
%%
%% Template by
%% Dr.-Ing. Erik Burger
%% burger@kit.edu
%%
%% Adaption by
%% Annika Vielsack
%% vielsack@kit.edu
%%
%% Version 1.0, 2021-07-03
\chapter{Introduction}
\label{ch:Introduction}


\section{Motivation}
\label{sec:Introduction:Motivation}

Blockchain represents one of the most popular trends in finance and computer science, 
during the last few years the number of investments has been growing exponentially. 
According \citet{CoinGeko}, the crypto market's value is standing around \$2 trillion.

Bitcoin can be considered the “father” of this technology. \citet{Bitcoin} depicted that in his paper, and in the early 2009,
it was effectively launched and the cryptocurrency Bitcoin was introduced. 
\citet{CoinGeko} states the value of Bitcoin around \$38,553.70 and its market capitalization more than  \$700 billions.

Many blockchain systems have been born with new capabilities, 
which have allowed them to fit many different use cases. The first, which allowed developers to 
code on top of itself, was Ethereum.
\citet{Ethereum} published its whitepaper in 2014, and in 2015 it was deployed.
The revolutionary aspect of Ethereum is the introduction of Smart Contract.
These are programs running on blockchain systems and give the developers the opportunity to interact directly 
with this new technology. 
The development of innovative and prominent applications is a consequence of their development, such as NFT marketplaces, music royalty tracking, supply chain and logistics monitoring, voting mechanism, 
cross-border payments, and many others.  

Interest in such a market has grown even among malicious attackers. 
Attacks such as the “Parity Wallet Hack” and the “Decentralized Autonomous Organization Attack” cost millions of dollars simply because of 
naive bugs in the smart contract code. Blockchain and smart contract technologies have multiple aims, but unfortunately, new applications 
based on them still contain bugs and multiple vulnerabilities, which cause 
several issues for the end-users. Most of the use of this technology relates to finance or certifications, therefore integrity, 
authentication and authorisation in transactions are mandatory. The research field behind blockchain technology is growing, as well as the one concerning 
its security and accordingly, many analysis tools were developed. 
These incorporate various strategies for performing the analyses, concerning the technical aspects of smart contracts, 
so these would work differently according to the object of the analysis. 

The topic that will be addressed in this thesis work is the analysis of smart contract security properties with the usage of tools. 
It involves the understanding of smart contracts properties and the comparison between different tools, 
providing insight regarding their behaviours in different contexts.


\section{Research Goals}
\label{sec:Introduction:ResearchGoals}
\paragraph{Research Question:} 
How do state-of-the-art analysis tools for Ethereum/Solidity perform (on different classes of properties/bugs)?

This thesis focuses on a dozen analytic tools, which we choose based on the type of analysis, trying to have a range of different typologies. 
We will test them on vulnerable smart contracts and figure out which properties are violated during real-world exploits. 
Furthermore, we are going to compare the tools, based on their performance, in particular, the criteria for the evaluation can cover the completeness of the analysis, the amount of found vulnerabilities and the number of false positive and negative. 
The execution time is crucial too, we want to understand how long it takes for finding a vulnerability. The time for the configuration and the report interpretability are parameters for defining how much a tool is user friendly. 

For answering the research question, we will give an answer to sub questions such as: 
\begin{itemize}
  \item How does a tool perform the analysis? 
  \item Which properties are relevant for smart contract security?
  \item Which ones have been violated in real-world exploits? 
  \item Which tools detect which class of vulnerabilities? 
\end{itemize}

\section{Research Approach}
\label{sec:Introduction:ResearchApproach}

\begin{table*}
  \caption{Gantt Chart Tasks}
      \label{tab:GanttChartTasks}
      \begin{tabular}{cc}
      \toprule
          Nunber & Name\\
          \midrule
          T1 & Research of real-world exploits and vulnerabilities\\
          T2 & Tools selection\\
          T3 & Installation and usage of tools \\
          T4 & Implementation of smart contracts\\
          T5 & Planning of the evaluation\\
          T6 & Testing smart contracts with tools\\
          T7 & Comparison of tools and properties \\
          T8 & Writing the thesis \\
      \bottomrule
      \end{tabular}
  \end{table*}

\begin{ganttchart}{1}{24}
  \gantttitle{Weekly Gantt Chart}{24} \\
  \gantttitlelist{1,...,24}{1} \\
  \ganttbar{T1}{1}{3} \\
  \ganttlinkedbar{T2}{2}{4} \\
  \ganttlinkedbar{T3}{4}{7} \\
  \ganttlinkedbar{T4}{6}{9} \\
  \ganttlinkedbar{T5}{9}{11} \\
  \ganttlinkedbar{T6}{12}{18} \\
  \ganttlinkedbar{T7}{18}{21} \\
  \ganttlinkedbar{T8}{8}{24} \\
\end{ganttchart}

\section{Releted Works}
\label{sec:Introduction:ReletedWorks}
Nowadays multiple surveys and research work addressing smart contracts analysis have been published. 
The ones, we are interested in, deal with the review of vulnerabilities, description and comparison of tools and definition of new techniques for scanning those. 

The selection of tools was anticipated by research work. 
We picked those starting from surveys and papers, 
regarding comparison of multiple of tools, such as \citet{Survey1}, \citet{Survey2}, \citet{Survey3}, \citet{Survey4}, \citet{thesis}. 
These give a general overview and provide a comparison based on different aspects: type of installation, running mode or type of analysis. 
A taxonomy is provided as well. 
For having a deeper knowledge of every single tool, we considered their papers and documentation.

In this thesis, we involved automated tools (\citet{Slither}, \citet {Mythril}) and the ones which provide the possibility to run custom analysis.
The first ones have as targets vulnerabilities such as reentrancy, overflow/underflow, and gas exceptions; but they do not provide functional correctness guarantees. 
On the other hand, the second group try to solve these issues by providing more possibilities for modelling the analyses. 
We involved tools adopting formal verification (\citet{CertoraDocumentation}, \citet{SolcVerify}, \citet{CelestialPaper}) and fuzzing (\citet{Echidna}). 

The cited works provide a comparison based on well-known benchmarks, defined vulnerabilities or just on the specifications.
This work provides a comparison between the considered tools as well, 
but we tried to move a step forward.
Rather than considering defined vulnerabilities, we consider real-world exploits, which have happened in the last couple of years.

The considered tools are installed and run on real-world attacks; these are chosen based on their effectiveness and the damage, in terms of drawn liquidity.